---
title: "Sherryx_FinalHomeworkCode_02"
author: "Sherry Xie"
date: "2025-02-10"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
---

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#loading ggplot for the figures
library(ggplot2)
```

```{r}
#loading prettydoc for the theme
library(prettydoc)
```

## 1. Probability of Hearing More than 8 Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear 8 or more calls over the original 15 calls
#1- because we want 8 or more calls
eight_or_more <- 1 - ppois(8, exact)

#show result
eight_or_more
```

## 2. Probability of Hearing No Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear no calls over the original 15 calls
#I did not use 1 - (100 percent chance of hearing call), because she heard no calls and there are no greater than...
#Listened from Amita and used dpois instead of ppois
no_call <- dpois(0, exact)

#show result
no_call
```

## 3. Probability of Hearing Exactly 3 Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear 3 calls over the original 15 calls
#No 1- because we want EXCATLY 3 calls
#Listened from Amita and used dpois instead of ppois
three_calls <- dpois(3, exact)

#show result
three_calls
```

## 4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30

```{r}
# this is the x values for the range 0 ≤ x ≤ 30
x_range <- 0:30
poisson_mass_function <- dpois(x_range, exact)

#provide a summary of the data: mean, median...
summary(poisson_mass_function)
```

```{r}
# Plot PMF
#Import the data created above
ggplot(data = data.frame(x_range, poisson_mass_function), aes(x = x_range, y = poisson_mass_function)) +
  
  #i need to fill the data otherwise nothing shows up on my figure
    geom_bar(stat = "identity", fill = "purple", alpha = 0.6) +
  
  #figure title and organization
    labs(title = "Poisson Probability Mass Function",
         x = "Number of Calls", y = "Probability") +
  
  #prettifying by using a theme
    theme_minimal()
```

## 5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
#originally resercher hears 15 calls
exact <- 15

# Simulate 104 Poisson-distributed monitoring sessions
#still over 15 as the original distribution: Average number of events per interval
# I used rpois: random density for poisson distribution instead of ppois which is probability distribution
stimulated_data <- rpois(104, exact)

#show result
stimulated_data

#provide a summary of the data: mean, median...
summary(stimulated_data)
```

## 6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
library(ggplot2)
# Plot histogram of simulated data
ggplot(data = data.frame(stimulated_data), aes(x = stimulated_data)) +
    geom_histogram(binwidth = 1, fill = "blue", alpha = 0.6, color = "black") +
   
  #labeling the graph
   labs(title = "Histogram of 104 Simulated Poisson Data",
         x = "Number of Calls", y = "Frequency") +
 
  #setting the horizontal limit from 0 to 30 
     xlim(0, 30) +
    theme_minimal()
```

-   The shape of the probability mass function I plotted above is 100% symmetrical

-   The simulated data still follows the overall trend of the PMF, but its not the same

    -   with some variations due to randomness of the 104 variables

    -   The histogram is therefore not symmetrical, bump on the left and right side

    -   this is a more accurate representation of what real life scientific data looks like
