---
title: "Sherryx_OriginalHomeworkCode_02"
author: "Sherry Xie"
date: "2025-02-07"
output: html_document
---

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#loading ggplot for the figures
library(ggplot2)
```

## 1. Probability of Hearing More than 8 Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear 8 or more calls over the original 15 calls
#1- because we want 8 or more calls
eight_or_more <- 1 - ppois(8, exact)

#show result
eight_or_more
```

## 2. Probability of Hearing No Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear no calls over the original 15 calls
#I did not use 1 - (100 percent chance of hearing call), because she heard no calls and there are no greater than...
no_call <- ppois(0, exact)

#show result
no_call
```

## 3. Probability of Hearing Exactly 3 Calls

```{r}
#originally resercher hears 15 calls
exact <- 15

#set up probability that she will hear 3 calls over the original 15 calls
#No 1- because we want EXCATLY 3 calls
three_calls <- ppois(3, exact)

#show result
three_calls
```

## 4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30

```{r}
# Generate values
x_values <- 0:30
poisson_pmf <- dpois(x_values, exact)

# Plot PMF
ggplot(data = data.frame(x_values, poisson_pmf), aes(x = x_values, y = poisson_pmf)) +
    geom_bar(stat = "identity", fill = "blue", alpha = 0.6) +
    labs(title = "Poisson Probability Mass Function (λ=15)",
         x = "Number of Calls", y = "Probability") +
    theme_minimal()

```

## 5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
set.seed(123)  # Ensure reproducibility
simulated_data <- rpois(10000, lambda)

# Plot histogram of simulated data
ggplot(data = data.frame(simulated_data), aes(x = simulated_data)) +
    geom_histogram(binwidth = 1, fill = "red", alpha = 0.6, color = "black") +
    labs(title = "Histogram of Simulated Poisson Data (λ=15)",
         x = "Number of Calls", y = "Frequency") +
    xlim(0, 30) +
    theme_minimal()
```

## 6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

-   The **theoretical Poisson distribution** predicts the probabilities well.

-   The **simulated data** follows the PMF closely, with some small variations due to randomness.
